\documentclass[12pt,a4paper]{report}
\usepackage{graphicx}       % For including images
\usepackage{amsmath}        % For math symbols
\usepackage{amssymb}        % For more math symbols
\usepackage{hyperref}       % For hyperlinks in the document
\usepackage{geometry}       % For adjusting margins
\geometry{left=3cm,right=3cm,top=2.5cm,bottom=2.5cm}
\usepackage{fancyhdr}       % For custom headers and footers
\usepackage{setspace}       % For line spacing

% Custom header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{University Report}
\fancyhead[R]{\thepage}

\begin{document}
	
	% Title Page
	\begin{titlepage}
		\centering
		\vspace*{2cm}
		
		\Huge
		\textbf{Scheduler Simulator}
		
		\vspace{1.5cm}
		
		\Large
		\textbf{Sahay Siddharth} \\
		\textbf{Ugarte Jordi}		
		
		\vfill
		
		\Large
		\textbf{Universite Libre de Bruxelles} \\
		\textbf{Real-Time Operative Systems}
		
		\vspace{0.8cm}
		
		\large
		\textbf{Submitted: \today}
		
		\vfill
	\end{titlepage}
	
	% Abstract
	\begin{abstract}
		This project involves designing a simulator of task executions with constrained deadlines. It consists in the implementation of three priority assignment algorithms: DM, EDF and Round Robin.
	\end{abstract}

	
	% Table of Contents
	\tableofcontents
	\newpage
	
	% List of Figures (if applicable)
	\listoffigures
	\newpage
	
	% List of Tables (if applicable)
	\listoftables
	\newpage
	
	% Introduction Chapter
	\chapter{Introduction}
	\section{Background}
	Provide the background of the report here.
	\section{Objective}
	State the main objectives of your work.
	\section{Structure of the Report}
	Briefly outline the structure of your report.
	
	% Main Body Chapters
	\chapter{Literature Review}
	Discuss relevant research and literature related to your topic.
	
	\chapter{Methodology}
	Explain the methods and tools you used in your research or project.
	
	\chapter{Results}
	Present the results or findings from your work.
	
	\chapter{Discussion}
	Interpret the results and compare them with previous work.
	
	\chapter{Conclusion}
	Summarize the key points of your report and discuss possible future work.
	
	% Bibliography/References
	\chapter*{References}
	\addcontentsline{toc}{chapter}{References}
	\bibliographystyle{plain}
	\bibliography{references}  % You can also enter references manually here
	
	% Appendix (if applicable)
	\appendix
	\chapter{Appendix A}
	Include supplementary material like raw data or additional figures.
	
\end{document}
